Market Simulator

### 2020-08-14 analysis/05_market_simulator.Rmd
fixed beta in persona reactive table and the data-width

    beta$p1_value <- 0
    beta$p1_value[beta$levels == 'Persona 1'] <- 1
    beta$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
    beta$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
    beta$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
    beta$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
    beta$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
    beta$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
    beta$p1_value[beta$levels %in% input$p1_family_activism] <- 1
    beta$p1_value[beta$levels %in% input$p1_religious_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_sport_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_art_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_labor_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_political_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_professional_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_other_member] <- 1
    beta$p1_value[beta$levels %in% input$p1_national_news] <- 1
    beta$p1_value[beta$levels %in% input$p1_international_news] <- 1
    beta$p1_value[beta$levels %in% input$p1_news_medium] <- 1
    beta$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
    beta$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
    beta$p1_value[beta$levels %in% input$p1_political_pref] <- 1
    beta$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
    beta$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
    beta$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
    beta$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
    beta$p1_value[beta$levels %in% input$p1_religion] <- 1
    beta$p1_value[beta$levels %in% input$p1_gender] <- 1
    beta$p1_value[beta$levels %in% input$p1_marital_status] <- 1
    beta$p1_value[beta$levels %in% input$p1_education] <- 1
    beta$p1_value[beta$levels %in% input$p1_income] <- 1
    beta$p1_value[beta$levels %in% input$p1_race] <- 1
    beta$p1_value[beta$levels %in% input$p1_age] <- 1

@@

    beta$p2_value <- 0
    beta$p2_value[beta$levels == 'Persona 2'] <- 1
    beta$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
    beta$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
    beta$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
    beta$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
    beta$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
    beta$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
    beta$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
    beta$p2_value[beta$levels %in% input$p2_family_activism] <- 1
    beta$p2_value[beta$levels %in% input$p2_religious_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_sport_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_art_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_labor_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_political_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_professional_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_other_member] <- 1
    beta$p2_value[beta$levels %in% input$p2_national_news] <- 1
    beta$p2_value[beta$levels %in% input$p2_international_news] <- 1
    beta$p2_value[beta$levels %in% input$p2_news_medium] <- 1
    beta$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
    beta$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
    beta$p2_value[beta$levels %in% input$p2_political_pref] <- 1
    beta$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
    beta$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
    beta$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
    beta$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
    beta$p2_value[beta$levels %in% input$p2_religion] <- 1
    beta$p2_value[beta$levels %in% input$p2_gender] <- 1
    beta$p2_value[beta$levels %in% input$p2_marital_status] <- 1
    beta$p2_value[beta$levels %in% input$p2_education] <- 1
    beta$p2_value[beta$levels %in% input$p2_income] <- 1
    beta$p2_value[beta$levels %in% input$p2_race] <- 1
    beta$p2_value[beta$levels %in% input$p2_age] <- 1

@@

    beta$p3_value <- 0
    beta$p3_value[beta$levels == 'Persona 3'] <- 1
    beta$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
    beta$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
    beta$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
    beta$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
    beta$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
    beta$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
    beta$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
    beta$p3_value[beta$levels %in% input$p3_family_activism] <- 1
    beta$p3_value[beta$levels %in% input$p3_religious_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_sport_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_art_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_labor_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_political_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_professional_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_other_member] <- 1
    beta$p3_value[beta$levels %in% input$p3_national_news] <- 1
    beta$p3_value[beta$levels %in% input$p3_international_news] <- 1
    beta$p3_value[beta$levels %in% input$p3_news_medium] <- 1
    beta$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
    beta$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
    beta$p3_value[beta$levels %in% input$p3_political_pref] <- 1
    beta$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
    beta$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
    beta$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
    beta$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
    beta$p3_value[beta$levels %in% input$p3_religion] <- 1
    beta$p3_value[beta$levels %in% input$p3_gender] <- 1
    beta$p3_value[beta$levels %in% input$p3_marital_status] <- 1
    beta$p3_value[beta$levels %in% input$p3_education] <- 1
    beta$p3_value[beta$levels %in% input$p3_income] <- 1
    beta$p3_value[beta$levels %in% input$p3_race] <- 1
    beta$p3_value[beta$levels %in% input$p3_age] <- 1
    beta

@@

Market Share Per Persona {data-height=600}
--------------------------------------

>>>>

    beta_persona$p1_value <- 0
    beta_persona$p1_value[beta$levels == 'Persona 1'] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta$levels %in% input$p1_age] <- 1

@@

    beta_persona$p2_value <- 0
    beta_persona$p2_value[beta$levels == 'Persona 2'] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_donation_amount] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_religious_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_environmental_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_travel_developing] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_religion_importance] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_gender] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta$levels %in% input$p2_age] <- 1

@@

    beta_persona$p3_value <- 0
    beta_persona$p3_value[beta$levels == 'Persona 3'] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta$levels %in% input$p3_age] <- 1
    beta_persona

@@

Market Share Per Persona
--------------------------------------
